---
title: "hw8"
author: "Kyu Park"
date: '2021 3 7 '
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r include=FALSE}
library(mosaic)
library(openintro)
```


## 1.

a) 
```{r}
data = na.omit(babies)
modg = lm(bwt~gestation, data = data)
summary(modg)
```
  i) $$SE = 16.74\sqrt{1+\frac{1}{1174}+\frac{(285-279)^2}{300687}} = 16.74812$$
```{r}
qt(0.025, 1173)
```
  $$CI =  -10.7541 + (0.4666)(285) \pm (1.961988)(16.74812) = (89.36728,155.08651)$$
  (89.36728,155.08651)
    
    
  ii)
  $$RSS = \sqrt{\frac{1}{1172}SSE} = 16.74, SSE = 328426.7472$$
  $$R^2 = \frac{SSR}{SST} = \frac{SST-SSE}{SST} = \frac{SST-328426.7472}{SST} = 0.1661$$
  $$SST = 393844.28252$$
      
    
b)
  i) Let $H_o$: $\beta = 0$ for all parameters and there is no correlation of baby's weight and whether mother smokes or not 
  $H_a$: $\beta \ne 0$ for any parameter, and there is some correlation of baby's weight and whether mother smokes or not
  ii) Since P<2e-16, at 95% confidence level, reject $H_o$; there is evidence to say that there is correlation of baby's weight and mother smoking.
  iii) $df = 1, F = \frac{328608-309075}{\frac{309075}{1171}} = 74.01$
  iv) Red dots are the data points of non-smoking mothers and green dots are the data points of smoking mothers.
  Solid line (regression equation for non-smoking mothers): $y = 0.45x - 3.18$
  Dotted line (regression equation for smoking mothers): $y = 0.45x - 3.18 - 8.37 = 0.45x - 11.55$ for y = baby weight and x = gestation.

c)
```{r}
modfull = lm(bwt~gestation+smoke+parity+age+height+weight, data = data)
summary(modfull)$coefficients #coefficients
summary(modfull)$sigma #residual standard error
summary(modfull)$df #degrees of freedom
```

  i) $y = -80.41 + 0.44g - 8.40s -3.33p - 0.01a + 1.15h + 0.05w$ where g = gestation, s = smoke, p = parity, a = age, h = height, w = weight.
  ii) For every 1 unit increase in gestation, the weight increases by 0.44 unit. For every 1 unit increase in smoke, the weight decreases by 8.40 unit. 
  iii) $$SSE = (RSE^2)(df) = 1167(15.83^2) = 292437$$
  $$SST = SSR + SSE = 292437 + 101649 =  394086$$
  iv) $$R^2 = \frac{SSR}{SST} = \frac{101649}{394086} = 0.2579$$
  $$Adjusted R^2 = 1-\frac{SSE/(n-7)}{SST/(n-1)} = 1-\frac{292437/1167}{394086/1173} = 0.25412$$

  v)
```{r}
res = (modfull$res - mean(modfull$res))/sd(modfull$res)
plot(modfull$fitted.values, res, xlab = "Predicted Values", ylab = "Residuals")
abline(h=0, col = "RED", lwd = 2)
```
  
```{r}
qqnorm(res, pch = 20)
qqline(res, col = "red")
```
  
  Model assumptions are satisfied, as they are normally distributed, have constant variance around 0 and show no clear pattern with no clear outlier. 
  

d)
```{r}
modpart = lm(bwt~gestation+smoke+parity+height, data = data)
anova(modpart, modfull)
```


  i) $H_o$: The coefficients of age and weight for baby’s weight are 0; no correlation of age and weight to baby's weight
 $H_a$: The coefficients of age and weight for baby’s weight are not 0; there is correlation of age and weight to baby's weight
  ii) Since Pr(>F) = 0.1377, at 95% confidence level, accept null hypothesis; there is no evidence to say that there is correlation of age and weight to body weight. 

  